---
title: "``cast_shadow_shift``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

Add a shadow and a ``shadow_shift`` column to a dataset

####  Description 

Shift the values and add a shadow column. It also respects the dplyr verbs ``starts_with``, ``contains``,
``ends_with``, etc.

####  Usage 
<pre><code>
cast_shadow_shift(data, ...)
</code></pre>
#### Arguments 

* data data.frame
* ... One or more unquoted variable names separated by commas. These respect the
dplyr verbs starts_with, contains, ends_with, etc.



#### Examples 
```{r}

airquality %>% cast_shadow_shift(Ozone)
airquality %>% cast_shadow_shift(Ozone,Temp)
airquality %>% cast_shadow_shift(dplyr::contains("o"))
```
#### Value 

data.frame with the shadow and shadow_shift vars

#### See Also 

cast_shadow_shift(), cast_shadow_shift_label() bind_shadow() add_any_miss() add_label_missings()
add_label_shadow() add_miss_cluster() add_prop_miss() add_shadow_shift()
