










---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

cast_shadow Add a shadow column to a dataset

####  Description 

Casting a shadow shifted column performs the equivalent pattern to data that makes it easy to perform certain visualisations, in line with the principle that the user should have a way to flexibly
return data formats containing information about the missing data. It forms the base building block for the functions ``cast_shadow_shift``, and ``cast_shadow_shift_label``. It also respects the dplyr
verbs starts_with, contains, ends_with, etc. to select variables.

####  Usage 
<pre><code>

cast_shadow(data, ...)
</code></pre>
#### Arguments 

* ``data``: data.frame
* ``...``: One or more unquoted variable names separated by commas. These respect the dplyr verbs starts_with, contains, ends_with, etc.

#### Value 

data with the added variable shifted and the suffix _NA

#### See Also 

cast_shadow_shift(), ``cast_shadow_shift_label()`` bind_shadow() ``add_any_miss()`` ``add_label_missings()``
add_label_shadow() ``add_miss_cluster()`` add_prop_miss() ``add_shadow_shift()``

#### Examples 
```{r}

airquality %>% cast_shadow(Ozone)
airquality %>% cast_shadow(Ozone, Solar.R)
library(ggplot2)
library(magrittr)
airquality %>%
cast_shadow(Ozone,Solar.R) %>%
ggplot(aes(x = Ozone,
colour = Solar.R_NA)) +
geom_density()
```


---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
cast_shadow_shift_label
Add a shadow column and a shadow shifted column to a dataset

####  Description 

Shift the values, add shadow, add missing label

####  Usage 
<pre><code>

cast_shadow_shift_label(data, ...)
</code></pre>
#### Arguments 

* ``data``: data.frame
... One or more unquoted expressions separated by commas. These also respect the dplyr verbs "starts_with", "contains", "ends_with", etc.

#### Value 

data.frame with the shadow and shadow_shift vars, and missing labels

#### See Also 

cast_shadow_shift(), cast_shadow_shift_label() bind_shadow() add_any_miss() add_label_missings()
add_label_shadow() add_miss_cluster() add_prop_miss() add_shadow_shift()

#### Examples 
```{r}

airquality %>% cast_shadow_shift_label(Ozone)
airquality %>% cast_shadow_shift_label(Ozone, Solar.R)
# replicate the plot generated by geom_miss_point()
library(ggplot2)
airquality %>%
cast_shadow_shift_label(Ozone,Solar.R) %>%
ggplot(aes(x = Ozone_shift,
common_na_numbers 21
y = Solar.R_shift,
colour = any_missing)) +
geom_point()
```

---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
common_na_strings Common string values for NA

####  Description 

This vector contains common values of NA (missing), which is aimed to be used inside naniar functions miss_scan_count() and replace_with_na(). The current list of strings used can be
found by printing out ``common_na_strings``. It is a useful way to explore your data for possible missings, but I strongly warn against using this to replace NA values without very carefully looking
at the incidence for each of the cases. Please note that common_na_strings uses \ around the "?", "." and "*" characters to protect against using their wildcard features in grep. Common NA numbers
are in the data object common_na_numbers.

####  Usage 
<pre><code>

common_na_strings
Format
An object of class character of length 24.
Note
original discussion here https://github.com/njtierney/naniar/issues/168

#### Examples 
```{r}

dat_ms <- tibble::tribble(~x, ~y, ~z,
1, "A", -100,
3, "N/A", -99,
NA, NA, -98,
-99, "E", -101,
-98, "F", -1)
miss_scan_count(dat_ms, -99)
miss_scan_count(dat_ms, c(-99,-98))
miss_scan_count(dat_ms, c("-99","-98","N/A"))
common_na_numbers
miss_scan_count(dat_ms, common_na_strings)
```

---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
GeomMissPoint naniar-ggproto

####  Description 

These are the stat and geom overrides using ggproto from ggplot2 that make naniar work.

####  Usage 
<pre><code>

StatMissPoint
</code></pre>

#### Format
An object of class StatMissPoint (inherits from Stat, ggproto, gg) of length 6.






---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
group_by_fun Group By Helper

####  Description 

This is a wrapper to facilitate the grouped_df S3 method.

####  Usage 
<pre><code>

group_by_fun(data, .fun, ...)
</code></pre>
#### Arguments 

* ``data``: data.frame, which will be grouped
* .fun a function to apply
* ... additional arguments to be passed to map

#### Value 

a dataframe with the function applied to each group

#### Examples 
```{r}

## Not run:
miss_case_table.grouped_df <- function(data){
group_by_fun(data,.fun = miss_case_table)
}
airquality %>%
group_by(Month) %>%
miss_case_table()
## End(Not run)
```


---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

``impute_below_at``: Scoped variants of impute_below

####  Description 

impute_below operates on all variables. To only impute variables that satisfy a specific condition, use the scoped variants, ``impute_below_at``, and ``impute_below_if``. To use _at effectively, you
must know that _at`` affects variables selected with a character vector, or with vars()'.

####  Usage 
<pre><code>

impute_below_at(.tbl, .vars, prop_below = 0.1, jitter = 0.05, ...)
</code></pre>
#### Arguments 

* .tbl a data.frame
* .vars variables to impute
* prop_below the degree to shift the values. default is
* jitter the amount of jitter to add. default is 0.05
* ... extra arguments

#### Value 

an dataset with values imputed

#### Examples 
```{r}

# select variables starting with a particular string.
library(dplyr)
impute_below_at(airquality,
.vars = c("Ozone", "Solar.R"))
impute_below_at(airquality,
.vars = 1:2)
#'
impute_below_at(airquality,
.vars = vars(Ozone))
## Not run:
library(ggplot2)
airquality %>%
bind_shadow() %>%
impute_below_at(vars(Ozone, Solar.R)) %>%
add_label_shadow() %>%
ggplot(aes(x = Ozone,
y = Solar.R,
colour = any_missing)) +
geom_point()
## End(Not run)
```

---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

impute_below_if Scoped variants of impute_below

####  Description 

impute_below operates on all variables. To only impute variables that satisfy a specific condition, use the scoped variants, ``impute_below_at``, and ``impute_below_if``.

####  Usage 
<pre><code>

impute_below_if(.tbl, .predicate, prop_below = 0.1, jitter = 0.05, ...)
36 impute_mean
</code></pre>
#### Arguments 

* ``.tbl``: data.frame
* ``.predicate``: A predicate function (such as is.numeric)
* ``prop_below``: the degree to shift the values. default is
* ``jitter``: the amount of jitter to add. default is 0.05
* ``...``: extra arguments

#### Value 

an dataset with values imputed

#### Examples 
```{r}

airquality %>%
impute_below_if(.predicate = is.numeric)
```

38 is_shade
is_shade Detect if this is a shade

####  Description 

This tells us if this column is a shade

####  Usage 
<pre><code>

is_shade(x)
are_shade(x)
any_shade(x)
</code></pre>
#### Arguments 

* ``x``: a vector you want to test if is a shade

#### Value 

logical - is this a shade?

#### Examples 
```{r}

xs <- shade(c(NA, 1, 2, "3"))
is_shade(xs)
are_shade(xs)
any_shade(xs)
aq_s <- as_shadow(airquality)
is_shade(aq_s)
are_shade(aq_s)
any_shade(aq_s)
any_shade(airquality)
```





---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

miss-complete-var-prop
Proportion of variables containing missings or complete values

####  Description 

Deprecated. Please see miss_var_prop() and complete_var_prop().

####  Usage 
<pre><code>

miss_var_prop(data)
complete_var_prop(data)
</code></pre>
#### Arguments 

* ``data``:  a dataframe

#### Value 

numeric the proportion of variables that contain missing or complete data


---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

miss_case_summary Summarise the missingness in each case

####  Description 

Provide a summary for each case in the data of the number, percent missings, and cumulative sum of missings of the order of the variables. By default, it orders by the most missings in each variable.

####  Usage 
<pre><code>

miss_case_summary(data, order = TRUE, add_cumsum = FALSE, ...)
</code></pre>
#### Arguments 

* ``data ``: a data.frame
* ``order``:  a logical indicating whether or not to order the result by n_miss. Defaults to TRUE. If FALSE, order of cases is the order input.
* ``add_cumsum``: logical indicating whether or not to add the cumulative sum of missings to the data. This can be useful when exploring patterns of nonresponse. These are calculated as the cumulative sum of the missings in the variables as they are first presented to the function.
* ``...``: extra arguments

#### Value 

a tibble of the percent of missing data in each case.

#### See Also 

pct_miss_case() prop_miss_case() pct_miss_var() prop_miss_var() pct_complete_case()
prop_complete_case() ``pct_complete_var()``,``prop_complete_var()``, miss_prop_summary() miss_
case_summary ``miss_var_table``, ``n_complete``, ``n_complete_row`` miss_var_run miss_var_span
miss_var_summary ``miss_var_table``, ``n_complete``, ``n_complete_row`` n_miss n_miss_row pct_
complete pct_miss ``prop_complete``, ``prop_complete_row``, ``prop_miss``

#### Examples 
```{r}

# works with group_by from dplyr
library(dplyr)
airquality %>%
group_by(Month) %>%
miss_case_summary()
miss_case_summary(airquality)
```


---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

``miss_case_table`` Tabulate missings in cases.

####  Description 

Provide a tidy table of the number of cases with 0, 1, 2, up to n, missing values and the proportion
of the number of cases those cases make up.

####  Usage 
<pre><code>

miss_case_table(data)
</code></pre>
#### Arguments 

* ``data``:  a dataframe

#### Value 

a dataframe



#### Examples 
```{r}

miss_case_table(airquality)
library(dplyr)
airquality %>%
group_by(Month) %>%
miss_case_table()
```


---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

miss_prop_summary Proportions of missings in data, variables, and cases.

####  Description 

Return missing data info about the dataframe, the variables, and the cases. Specifically, returning
how many elements in a dataframe contain a missing value, how many elements in a variable contain
a missing value, and how many elements in a case contain a missing.
miss_scan_count 47

####  Usage 
<pre><code>

miss_prop_summary(data)
</code></pre>
#### Arguments 

* ``data``:  a dataframe

#### Value 

a dataframe



#### Examples 
```{r}

miss_prop_summary(airquality)
library(dplyr)
airquality %>% group_by(Month) %>% miss_prop_summary()
```

---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

miss_scan_count Search and present different kinds of missing values

####  Description 

Searching for different kinds of missing values is really annoying. If you have values like -99 in your data, when they shouldn't be there, or they should be encoded as missing, it can be difficult to
ascertain if they are there, and if so, where they are. miss_scan_count makes it easier for users to search for particular occurrences of these values across their variables.

####  Usage 
<pre><code>

miss_scan_count(data, search)
</code></pre>
#### Arguments 

* ``data``: data
* ``search``:  values to search for

#### Value 

a dataframe of the occurrences of the values you searched for
48 miss_summary

#### See Also 

pct_miss_case() prop_miss_case() pct_miss_var() prop_miss_var() pct_complete_case()
prop_complete_case() ``pct_complete_var()``,``prop_complete_var()``, miss_prop_summary() miss_
case_summary ``miss_var_table``, ``n_complete``, ``n_complete_row`` miss_var_run miss_var_span
miss_var_summary miss_var_table

#### Examples 
```{r}

dat_ms <- tibble::tribble(~x, ~y, ~z,
1, "A", -100,
3, "N/A", -99,
NA, NA, -98,
-99, "E", -101,
-98, "F", -1)
miss_scan_count(dat_ms,-99)
miss_scan_count(dat_ms,c(-99,-98))
miss_scan_count(dat_ms,c("-99","-98","N/A"))
miss_scan_count(dat_ms,common_na_strings)
```


---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

miss_summary Collate summary measures from naniar into one tibble

####  Description 

miss_summary performs all of the missing data helper summaries and puts them into lists within a
tibble

####  Usage 
<pre><code>

miss_summary(data, order = TRUE)
</code></pre>
#### Arguments 

* ``data``:  a dataframe
order whether or not to order the result by n_miss
... extra arguments

#### Value 

a tibble of missing data summaries


#### Examples 
```{r}

s_miss <- miss_summary(airquality)
s_miss$miss_df_prop
s_miss$miss_case_table
s_miss$miss_var_summary
# etc, etc, etc.
library(dplyr)
s_miss_group <- group_by(airquality, Month) %>% miss_summary()
s_miss_group$miss_df_prop
s_miss_group$miss_case_table
# etc, etc, etc.
```

---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
miss_var_run Find the number of missing and complete values in a single run

####  Description 

It us useful to find the number of missing values that occur in a single run. The function, miss_var_run(), returns a dataframe with the column names "run_length" and "is_na", which describe the length of
the run, and whether that run describes a missing value.

####  Usage 
<pre><code>

miss_var_run(data, var)
</code></pre>

#### Arguments 

* ``data``: data.frame
* ``var``: a bare variable name

#### Value 

dataframe with column names "run_length" and "is_na", which describe the length of the run, and whether that run describes a missing value.

#### Examples 

```{r}

miss_var_run(pedestrian, hourly_counts)
library(dplyr)
# find the number of runs missing/complete for each month
pedestrian %>%
group_by(month) %>%
miss_var_run(hourly_counts)
library(ggplot2)
# explore the number of missings in a given run
miss_var_run(pedestrian, hourly_counts) %>%
filter(is_na == "missing") %>%
count(run_length) %>%
ggplot(aes(x = run_length,
y = n)) +
geom_col()
# look at the number of missing values and the run length of these.
miss_var_run(pedestrian, hourly_counts) %>%
ggplot(aes(x = is_na,
y = run_length)) +
geom_boxplot()
# using group_by
pedestrian %>%
group_by(month) %>%
miss_var_run(hourly_counts)
```



---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```






naniar naniar

####  Description 

naniar is a package to make it easier to summarise and handle missing values in R. It strives to do
this in a way that is as consistent with tidyverse principles as possible.




---
title: "``naniar::n_complete``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

Return the number of complete values

####  Description 

A complement to ``n_miss``

####  Usage 
<pre><code>

n_complete(x)
</code></pre>
#### Arguments 

* ``x``: a vector

#### Value 

numeric number of complete values

#### Examples 
```{r}

n_complete(airquality)
n_complete(airquality$Ozone)
```




---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

Return the number of missing values

####  Description 

Substitute for sum(is.na(data))

####  Usage 
<pre><code>

n_miss(x)
</code></pre>
#### Arguments 

* ``x``: a vector

#### Value 

numeric the number of missing values

#### Examples 
```{r}

n_miss(airquality)
n_miss(airquality$Ozone)
```

---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

## oceanbuoys 

West Pacific Tropical Atmosphere Ocean Data, 1993 & 1997.

####  Description 

Real-time data from moored ocean buoys for improved detection, understanding and prediction of El Ni'o and La Ni'a. The data is collected by the Tropical Atmosphere Ocean project (http:
//www.pmel.noaa.gov/tao/index.shtml).

####  Usage 
<pre><code>
data(oceanbuoys)
</code></pre>

Format
An object of class tbl_df (inherits from tbl, data.frame) with 736 rows and 8 columns.

#### Details
Format: a data frame with 736 observations on the following 8 variables.

* ``year``: A numeric with levels 1993 1997.
* ``latitude``: A numeric with levels -5 -2 0.
* ``longitude``: A numeric with levels -110 -95.
* ``sea_temp_c``: Sea surface temperature(degree Celsius), measured by the TAO buoys at one meter
below the surface.
* ``air_temp_c``: Air temperature(degree Celsius), measured by the TAO buoys three meters above the
sea surface.
* ``humidity``: Relative humidity( meters above the sea surface.
* ``wind_ew``: The East-West wind vector components(M/s). TAO buoys measure the wind speed and direction four meters above the sea surface. If it is positive, the East-West component of the
wind is blowing towards the East. If it is negative, this component is blowing towards the West.
* ``wind_ns``: The North-South wind vector components(M/s). TAO buoys measure the wind speed and direction four meters above the sea surface. If it is positive, the North-South component of the
wind is blowing towards the North. If it is negative, this component is blowing towards the South.

#### Source
http://www.pmel.noaa.gov/tao/data_deliv/deliv.html

#### See Also 

library(MissingDataGUI) (data named "tao")

#### Examples 
```{r}

# explore the missingness with vis_miss
library(naniar)
vis_miss(oceanbuoys)
# Look at the missingness in the variables
miss_var_summary(oceanbuoys)
# Look at the missingness in air temperature and humidity
library(ggplot2)
p <-
ggplot(oceanbuoys,
aes(x = air_temp_c,
pct-miss-complete-case 63
y = humidity)) +
geom_miss_point()
p
# for each year?
p + facet_wrap(~year)
# this shows that there are more missing values in humidity in 1993, and
# more air temperature missing values in 1997
# what if we explore the value of air temperature and humidity based on
# the missingness of each
oceanbuoys %>%
bind_shadow() %>%
ggplot(aes(x = air_temp_c,
fill = humidity_NA)) +
geom_histogram()
oceanbuoys %>%
bind_shadow() %>%
ggplot(aes(x = humidity,
fill = air_temp_c_NA)) +
geom_histogram()
```



---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

replace_to_na Replace values with missings

####  Description 

This function is deprecated, please see replace_with_na().

####  Usage 
<pre><code>

replace_to_na(data, to_na = list(), ...)

</code></pre>
#### Arguments 

* ``data``: A data.frame
* ``to_na``: A named list given the NA to replace values
* ``...``: additional arguments for methods.

#### Value 

values replaced by NA






---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

``shadow_shift.numeric`` 
Shift (impute) numeric values for graphical exploration

####  Description 

Shift (impute) numeric values for graphical exploration

####  Usage 
<pre><code>

## S3 method for class 'numeric'
shadow_shift(x, prop_below = 0.1, jitter = 0.05,
seed_shift = 2017 - 7 - 1 - 1850, ...)
</code></pre>
#### Arguments 

* ``x``: a variable of interest to shift
* ``prop_below``: the degree to shift the values. default is
* ``jitter``: the amount of jitter to add. default is 0.05
* ``seed_shift``: a random seed to set, if you like
* ``...``: extra arguments to pass



---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

test_if_shadow Test if input is a shadow

####  Description 

Test if input is a shadow

####  Usage 
<pre><code>

test_if_shadow(x)
</code></pre>
#### Arguments 

x object
90 unbinders

#### Value 

an error if input (x) is a shadow

#### Examples 
```{r}

## Not run:
# success
aq_shadow <- bind_shadow(airquality)
test_if_shadow(aq_shadow)
#fail
test_if_shadow(airquality)

```


---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
update_shadow Expand all shadow levels

####  Description 

Internal function to appropriately expand and relevel all shadow variables to include a new suffix

####  Usage 
<pre><code>

update_shadow(data, suffix)
</code></pre>
#### Arguments 

* ``data``: data.frame
suffix character vector

#### Value 

data.frame with adjusted levels

#### Examples 
```{r}

df <- tibble::tribble(
~wind, ~temp,
-99, 45,
68, NA,
72, 25
)
dfs <- bind_shadow(df)
update_shadow(dfs, "weee")
update_shadow(dfs, "weee") %>% what_levels()
## End(Not run)
```


---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
what_levels check the levels of many things

####  Description 

this function is used internally to check what the levels are of the dataframe.

####  Usage 
<pre><code>

what_levels(x)
</code></pre>
#### Arguments 

x data.frame, usually

#### Value 

a list containing the levels of everything


---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
## where 

Split a call into two components with a useful verb name

####  Description 

This function is used inside recode_shadow to help evaluate the formula call effectively. .where is
a special function designed for use in recode_shadow, and you shouldn't use it outside of it

####  Usage 
<pre><code>

.where(...)
</code></pre>
#### Arguments 

... case_when style formula

#### Value 

a list of "condition" and "suffix" arguments
where_na 93

#### Examples 
```{r}

## Not run:
df <- tibble::tribble(
~wind, ~temp,
-99, 45,
68, NA,
72, 25
)
dfs <- bind_shadow(df)
recode_shadow(dfs,
temp = .where(wind == -99 ~ "bananas"))
## End(Not run)
```


---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
where_na Which rows and cols contain missings?

####  Description 

Internal function that is short for which(is.na(x), arr.ind = TRUE). Creates array index locations of missing values in a dataframe.

####  Usage 
<pre><code>

where_na(x)
</code></pre>

#### Arguments 

* ``x``: a dataframe

#### Value 

a matrix with columns "row" and "col", which refer to the row and column that identify the position
of a missing value in a dataframe

#### See Also 

which_na()

#### Examples 
```{r}

where_na(airquality)
where_na(oceanbuoys$sea_temp_c)
```


---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
which_are_shade Which variables are shades?

####  Description 

This function tells us which variables contain shade information

####  Usage 
<pre><code>

which_are_shade(.tbl)
</code></pre>
#### Arguments 

.tbl a data.frame or tbl

#### Value 

numeric - which column numbers contain shade information

#### Examples 
```{r}

df_shadow <- bind_shadow(airquality)
```

---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
## which_are_shade(df_shadow)
which_na Which elements contain missings?

####  Description 

Equivalent to ``which(is.na())`` - returns integer locations of missing values.

####  Usage 
<pre><code>

which_na(x)
</code></pre>
#### Arguments 

* ``x``: a dataframe

#### Value 

integer locations of missing values.


#### See Also 

where_na()

#### Examples 
```{r}

which_na(airquality)
```

