---
title: "``naniar::add_any_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```


Add a column describing presence of any missing values

####  Description 

This adds a column named "any_miss" (by default) that describes whether there are any missings
in all of the variables (default), or whether any of the specified columns, specified using variables
names or dplyr verbs, starts_with, contains, ends_with, etc. By default the added column will
be called "any_miss_all", if no variables are specified, otherwise, if variables are specified, the label
will be "any_miss_vars" to indicate that not all variables have been used to create the labels.

####  Usage 
<pre><code>

add_any_miss(data, ..., label = "any_miss", missing = "missing",
complete = "complete")
</code></pre>
#### Arguments 

* ``data``: data.frame
* ``...``: Variable names to use instead of the whole dataset. By default this looks at the whole dataset. Otherwise, this is one or more unquoted expressions separated by commas. These also respect the dplyr verbs starts_with, contains, ends_with, etc. By default will add "_all" to the label if left blank, otherwise will add "_vars" to distinguish that it has not been used on all of the variables.
* ``label``: label for the column, defaults to "any_miss". By default if no additional variables are listed the label col is "any_miss_all", otherwise it is "any_miss_vars",
if variables are specified.
* ``missing``: character a label for when values are missing - defaults to "missing" complete * ``character``: character a label for when values are complete - defaults to "complete" 

#### Details
By default the prefix "any_miss" is used, but this can be changed in the label argument.

#### Value 

data.frame with data and the column labelling whether that row (for those variables) has any missing
values - indicated by "missing" and "complete".

#### See Also 

bind_shadow() add_any_miss() add_label_missings() add_label_shadow() add_miss_cluster()
add_n_miss() add_prop_miss() add_shadow_shift() cast_shadow()


#### Examples 
```{r}

airquality %>% add_any_miss()
airquality %>% add_any_miss(Ozone)
airquality %>% add_any_miss(Ozone, Solar.R)
```
