---
title: "``naniar::add_miss_cluster``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

 Add a column that tells us which "missingness cluster" a row belongs to

####  Description 

A way to extract the cluster of missingness that a group belongs to. For example, if you use vis_miss(airquality, cluster = TRUE), you can see some clustering in the data, but you do not have a way to identify the cluster. Future work will incorporate the seriation package to allow for better control over the clustering from the user.

####  Usage 
<pre><code>

add_miss_cluster(data, cluster_method = "mcquitty", n_clusters = 2)
</code></pre>
#### Arguments 

* ``data``:  a dataframe
* ``cluster_method``: character vector of the agglomeration method to use, the default is "mcquitty".
Options are taken from stats::hclust helpfile, and options include: "ward.D",
"ward.D2", "single", "complete", "average" (= UPGMA), "mcquitty" (= WPGMA),
"median" (= WPGMC) or "centroid" (= UPGMC).
* ``n_clusters``: numeric the number of clusters you expect. Defaults to 2.


#### Examples 
```{r}

add_miss_cluster(airquality)
add_miss_cluster(airquality, cluster_method = "ward.D")
add_miss_cluster(airquality, cluster_method = "ward.D", n_clusters = 3)
add_miss_cluster(airquality, n_clusters = 3)
```
