---
title: "``add_shadow_shift ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

 Add a shadow shifted column to a dataset

####  Description 

Shadow shift missing values using only the selected variables in a dataset, by specifying variable
names or use dplyr vars and dplyr verbs starts_with, contains, ends_with, etc.

####  Usage 
<pre><code>

add_shadow_shift(data, ..., suffix = "shift")
</code></pre>
#### Arguments 

* ``data``: data.frame
* ``...``: One or more unquoted variable names separated by commas. These also respect the dplyr verbs starts_with, contains, ends_with, etc.
suffix suffix to add to variable, defaults to "shift"

#### Value 

data with the added variable shifted named as var_suffix
12 add_span_counter

#### See Also 

bind_shadow() add_any_miss() add_label_missings() add_label_shadow() add_miss_cluster()
add_n_miss() add_prop_miss() add_shadow_shift() cast_shadow()

#### Examples 
```{r}

pedestrian %>% add_shadow_shift(hourly_counts)
airquality %>% add_shadow_shift(Ozone, Solar.R)
```
