
---
title: "``naniar::bind_shadow``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

``bind_shadow`` 

Bind a shadow dataframe to original data

####  Description 

Binding a shadow matrix to a regular dataframe helps visualise and work with missing data.

####  Usage 
<pre><code>

bind_shadow(data, only_miss = FALSE, ...)
</code></pre>
#### Arguments 

* ``data``:  a dataframe
* only_miss logical - if FALSE (default) it will bind a dataframe with all of the variables duplicated with their shadow. Setting this to TRUE will bind variables only
those variables that contain missing values. See the examples for more details.
* ... extra options to pass to recode_shadow() - a work in progress.

#### Value 

data with the added variable shifted and the suffix _NA


#### Examples 
```{r}

bind_shadow(airquality)
# bind only the variables that contain missing values
bind_shadow(airquality, only_miss = TRUE)
aq_shadow <- bind_shadow(airquality)
# explore missing data visually
```
```{r}
library(ggplot2)
# using the bounded shadow to visualise Ozone according to whether Solar
# Radiation is missing or not.
ggplot(data = aq_shadow,
aes(x = Ozone)) +
geom_histogram() +
facet_wrap(~Solar.R_NA,
ncol = 1)
```

