---
title: "``naniar::cast_shadow_shift_label``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
cast_shadow_shift_label
Add a shadow column and a shadow shifted column to a dataset

####  Description 

Shift the values, add shadow, add missing label

####  Usage 
<pre><code>

cast_shadow_shift_label(data, ...)
</code></pre>
#### Arguments 

* ``data``: data.frame
... One or more unquoted expressions separated by commas. These also respect the dplyr verbs "starts_with", "contains", "ends_with", etc.

#### Value 

data.frame with the shadow and shadow_shift vars, and missing labels


#### Examples 
```{r}

airquality %>% cast_shadow_shift_label(Ozone)
airquality %>% cast_shadow_shift_label(Ozone, Solar.R)
# replicate the plot generated by geom_miss_point()
library(ggplot2)
airquality %>%
cast_shadow_shift_label(Ozone,Solar.R) %>%
ggplot(aes(x = Ozone_shift,
common_na_numbers 21
y = Solar.R_shift,
colour = any_missing)) +
geom_point()
```
