---
title: "``common_na_numbers ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

Common number values for NA

####  Description 

This vector contains common number values of NA (missing), which is aimed to be used inside naniar
functions ``miss_scan_count()`` and ``replace_with_na()``. The current list of numbers can be
found by printing out common_na_numbers. It is a useful way to explore your data for possible missings,
but I strongly warn against using this to replace NA values without very carefully looking at
the incidence for each of the cases. Common NA strings are in the data object ``common_na_strings``.

####  Usage 
<pre><code>

common_na_numbers
</code></pre>

#### Format
An object of class numeric of length 8.

#### Note
original discussion here https://github.com/njtierney/naniar/issues/168

#### Examples 
```{r}

dat_ms <- tibble::tribble(~x, ~y, ~z,
1, "A", -100,
3, "N/A", -99,
NA, NA, -98,
-99, "E", -101,
-98, "F", -1)
miss_scan_count(dat_ms, -99)
miss_scan_count(dat_ms, c(-99,-98))
miss_scan_count(dat_ms, c("-99","-98","N/A"))
common_na_numbers
miss_scan_count(dat_ms, common_na_numbers)
```