--
title: "``naniar::common_na_strings``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
 Common string values for NA

####  Description 

This vector contains common values of NA (missing), which is aimed to be used inside naniar functions miss_scan_count() and replace_with_na(). The current list of strings used can be found by printing out ``common_na_strings``. It is a useful way to explore your data for possible missings, but I strongly warn against using this to replace NA values without very carefully looking
at the incidence for each of the cases. Please note that common_na_strings uses \ around the "?", "." and "*" characters to protect against using their wildcard features in grep. Common NA numbers
are in the data object common_na_numbers.

####  Usage 
<pre><code>

common_na_strings
</code></pre>

#### Format
An object of class character of length 24.

#### Note
original discussion here https://github.com/njtierney/naniar/issues/168

#### Examples 
```{r}

dat_ms <- tibble::tribble(~x, ~y, ~z,
1, "A", -100,
3, "N/A", -99,
NA, NA, -98,
-99, "E", -101,
-98, "F", -1)
miss_scan_count(dat_ms, -99)
miss_scan_count(dat_ms, c(-99,-98))
miss_scan_count(dat_ms, c("-99","-98","N/A"))
common_na_numbers
miss_scan_count(dat_ms, common_na_strings)
```
