---
title: "``naniar::gg_miss_case``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

Plot the number of missings per case (row)

####  Description 

This is a visual analogue to miss_case_summary. It draws a ggplot of the number of missings in
each case (row). A default minimal theme is used, which can be customised as normal for ggplot.

####  Usage 
<pre><code>
gg_miss_case(x, facet, order_cases = TRUE, show_pct = FALSE)
</code></pre>

#### Arguments 

* ``x``: data.frame
* ``facet``: (optional) a single bare variable name, if you want to create a faceted plot.
* ``order_cases``: logical Order the rows by missingness (default is FALSE - no order).
* ``show_pct``: logical Show the percentage of cases

#### Value 

a ggplot object depicting the number of missings in a given case.

#### See Also 

``geom_miss_point()``,``gg_miss_case_cumsum``,``gg_miss_fct()``,``gg_miss_span()``,``gg_miss_var()``,
``gg_miss_var_cumsum()``,``gg_miss_which()``

#### Examples 
```{r}

gg_miss_case(airquality)
library(ggplot2)
gg_miss_case(airquality) + labs(x = "Number of Cases")
gg_miss_case(airquality, show_pct = TRUE)
gg_miss_case(airquality, order_cases = FALSE)
gg_miss_case(airquality, facet = Month)
gg_miss_case(airquality, facet = Month, order_cases = FALSE)
gg_miss_case(airquality, facet = Month, show_pct = TRUE)
```