---
title: "``gg_miss_var``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
Plot the number of missings for each variable

####  Description 

This is a visual analogue to miss_var_summary. It draws a ggplot of the number of missings in each
variable, ordered to show which variables have the most missing data. A default minimal theme is
used, which can be customised as normal for ggplot.

####  Usage 
<pre><code>
gg_miss_var(x, facet, show_pct = FALSE)
</code></pre>
#### Arguments 

* ``x``: a dataframe
* ``facet``: (optional) bare variable name, if you want to create a faceted plot.
* ``show_pct``: logical shows the number of missings (default), but if set to TRUE, it will display the proportion of missings.



#### Examples 
```{r}

gg_miss_var(airquality)
library(ggplot2)
gg_miss_var(airquality) + labs(y = "Look at all the missing ones")
gg_miss_var(airquality, Month)
gg_miss_var(airquality, Month, show_pct = TRUE)
gg_miss_var(airquality, Month, show_pct = TRUE) + ylim(0, 100)
```

#### Value 

a ggplot object depicting the number of missings in a given column

#### See Also 

geom_miss_point() gg_miss_case() gg_miss_case_cumsum gg_miss_fct() gg_miss_span()
gg_miss_var() gg_miss_var_cumsum() gg_miss_which()