---
title: "``gg_miss_span``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

Plot the number of missings in a given repeating span

####  Description 

``gg_miss_span`` is a replacement function to ``imputeTS::plotNA.distributionBar(tsNH4, breaksize = 100)``,
which shows the number of missings in a given span, or breaksize. A default minimal theme is used,
which can be customised as normal for ggplot.

####  Usage 
<pre><code>

gg_miss_span(data, var, span_every, facet)
</code></pre>
#### Arguments 

* ``data``: data.frame
* ``var``: a bare unquoted variable name from data.
* ``span_every``: integer describing the length of the span to be explored
* ``facet``: (optional) a single bare variable name, if you want to create a faceted plot.


#### Examples 
```{r}

miss_var_span(pedestrian, hourly_counts, span_every = 3000)
library(ggplot2)
gg_miss_span(pedestrian, hourly_counts, span_every = 3000)
gg_miss_span(pedestrian, hourly_counts, span_every = 3000, facet = sensor_name)
# works with the rest of ggplot
gg_miss_span(pedestrian, hourly_counts, span_every = 3000) + labs(x = "custom")
gg_miss_span(pedestrian, hourly_counts, span_every = 3000) + theme_dark()
gg_miss_span(pedestrian, hourly_counts, span_every = 3000, facet = sensor_name)
```


#### Value 

ggplot2 showing the number of missings in a span (window, or breaksize)

#### See Also 

``geom_miss_point()``,``gg_miss_case()``,``gg_miss_case_cumsum``,``gg_miss_fct()``,``gg_miss_var()``,
``gg_miss_var_cumsum()``,``gg_miss_which()``