---
title: "``gg_miss_upset``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

Plot the pattern of missingness using an upset plot.

####  Description 

Upset plots are a way of visualising common sets, gg_miss_upset`` shows the number of missing values for each of = 5means to look at 5 variables and their combinations. The number of combinations or ratherintersectionsis = 10to look at 10 sets of variables, andnintersects = 50' to look at 50 intersections.

####  Usage 
<pre><code>

gg_miss_upset(data, order.by = "freq", ...)
</code></pre>
#### Arguments 

* ``data``: data.frame
* ``order.by``: (from UpSetR::upset) How the intersections in the matrix should be ordered by.
Options include frequency (entered as "freq"), degree, or both in any order. See ``?UpSetR::upset`` for more options
* ``...``: arguments to pass to upset plot - see ?UpSetR::upset

#### Value 

a ggplot visualisation of missing data

#### Examples 
```{r}

## Not run:
gg_miss_upset(airquality)
gg_miss_upset(pedestrian)
```


```{r}
gg_miss_upset(riskfactors)
gg_miss_upset(riskfactors, nsets = 10)
gg_miss_upset(riskfactors, nsets = 10, nintersects = 10)
## End(Not run)
```