---
title: "``impute_below_all``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

Impute data with values shifted 10% below range.

####  Description 

It can be useful in exploratory graphics to impute data outside the range of the data. ``impute_below_all``
imputes all variables with missings to have values 10 values adds a new string or label.

####  Usage 
<pre><code>

impute_below_all(.tbl, prop_below = 0.1, jitter = 0.05, ...)
</code></pre>
#### Arguments 

* ``.tbl``: a data.frame
* ``prop_below``: the degree to shift the values. default is
* ``jitter``: the amount of jitter to add. default is 0.05
* ``...``: additional arguments

#### Value 

an dataset with values imputed


#### Examples 
```{r}

# you can impute data like so:
airquality %>%
impute_below_all()
```

```{r}
# However, this does not show you WHERE the missing values are.
# to keep track of them, you want to use `bind_shadow()` first.
airquality %>%
bind_shadow() %>%
impute_below_all()
# This identifies where the missing values are located, which means you
# can do things like this:
```

```{r}
library(ggplot2)
airquality %>%
bind_shadow() %>%
impute_below_all() %>%
# identify where there are missings across rows.
add_label_shadow() %>%
ggplot(aes(x = Ozone,
y = Solar.R,
colour = any_missing)) +
geom_point()
# Note that this ^^ is a long version of `geom_miss_point()`.
```
