---
title: "``label_missings``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
 Is there a missing value in the row of a dataframe?

####  Description 

Creates a character vector describing presence/absence of missing values

####  Usage 
<pre><code>

label_missings(data, ..., missing = "Missing",
complete = "Not Missing")

</code></pre>
#### Arguments 

* ``data``:  a dataframe or set of vectors of the same length
* ``...``: extra variable to label
* ``missing``: character a label for when values are missing - defaults to "Missing"
* ``complete``: character character a label for when values are complete - defaults to "Not Missing"

#### Value 

character vector of "Missing" and "Not Missing".

#### See Also 

``bind_shadow()`` ``add_any_miss()`` ``add_label_missings()`` ``add_label_shadow()`` ``add_miss_cluster()``
``add_n_miss()`` ``add_prop_miss()`` ``add_shadow_shift()`` ``cast_shadow()``

#### Examples 
```{r}

label_missings(airquality)
library(dplyr)
airquality %>%
mutate(is_missing = label_missings(airquality)) %>%
head()

```

```{r}

airquality %>%
mutate(is_missing = label_missings(airquality,
missing = "definitely missing",
complete = "absolutely complete")) %>%
head()
```