---
title: "``naniar::miss_var_summary``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)

```
miss_var_summary Summarise the missingness in each variable

####  Description 

Provide a summary for each variable of the number, percent missings, and cumulative sum of missings of the order of the variables. By default, it orders by the most missings in each variable.

####  Usage 
<pre><code>

miss_var_summary(data, order = FALSE, add_cumsum = FALSE, ...)
</code></pre>
#### Arguments 

* ``data ``: a data.frame
* ``order``:  a logical indicating whether to order the result by n_miss. Defaults to TRUE. If FALSE, order of variables is the order input.
* ``add_cumsum``: logical indicating whether or not to add the cumulative sum of missings to the data. This can be useful when exploring patterns of nonresponse. These are
calculated as the cumulative sum of the missings in the variables as they are first presented to the function.
* ``...``: extra arguments

#### Value 

a tibble of the percent of missing data in each variable

#### Note
n_miss_cumsum is calculated as the cumulative sum of missings in the variables in the order that
they are given in the data when entering the function


#### Examples 

```{r}

miss_var_summary(airquality)
miss_var_summary(oceanbuoys, order = TRUE)
# works with group_by from dplyr
```


```{r}
library(dplyr)

airquality %>%
  group_by(Month) %>%
  miss_var_summary()
```
