
---
title: "``naniar::n_miss``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

miss_scan_count Search and present different kinds of missing values

####  Description 

Searching for different kinds of missing values is really annoying. If you have values like -99 in your data, when they shouldn't be there, or they should be encoded as missing, it can be difficult to
ascertain if they are there, and if so, where they are. miss_scan_count makes it easier for users to search for particular occurrences of these values across their variables.

####  Usage 
<pre><code>

miss_scan_count(data, search)
</code></pre>
#### Arguments 

* ``data``: data
* ``search``:  values to search for

#### Value 

a dataframe of the occurrences of the values you searched for
48 miss_summary

#### See Also 

pct_miss_case() prop_miss_case() pct_miss_var() prop_miss_var() pct_complete_case()
prop_complete_case() ``pct_complete_var()``,``prop_complete_var()``, miss_prop_summary() miss_
case_summary ``miss_var_table``, ``n_complete``, ``n_complete_row`` miss_var_run miss_var_span
miss_var_summary miss_var_table

#### Examples 
```{r}

dat_ms <- tibble::tribble(~x, ~y, ~z,
1, "A", -100,
3, "N/A", -99,
NA, NA, -98,
-99, "E", -101,
-98, "F", -1)
miss_scan_count(dat_ms,-99)
miss_scan_count(dat_ms,c(-99,-98))
miss_scan_count(dat_ms,c("-99","-98","N/A"))
miss_scan_count(dat_ms,common_na_strings)
```
