
---
title: "``naniar::n_miss_row``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

n_miss_row Return a vector of the number of missing values in each row

####  Description 

Substitute for rowSums(is.na(data)), but it also checks if input is NULL or is a dataframe

####  Usage 
<pre><code>

n_miss_row(data)
</code></pre>
#### Arguments 

* ``data``:  a dataframe

#### Value 

numeric vector of the number of missing values in each row

#### See Also 

pct_miss_case() prop_miss_case() pct_miss_var() prop_miss_var() pct_complete_case()
prop_complete_case() ``pct_complete_var()``,``prop_complete_var()``, miss_prop_summary() miss_
case_summary ``miss_var_table``, ``n_complete``, ``n_complete_row`` miss_var_run miss_var_span
miss_var_summary ``miss_var_table``, ``n_complete``, ``n_complete_row`` n_miss n_miss_row pct_
complete pct_miss ``prop_complete``, ``prop_complete_row``, ``prop_miss``

#### Examples 
```{r}

n_miss_row(airquality)
