---
title: "``Pedestrian``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Pedestrian count information around Melbourne for 2016

####  Description 

This dataset contains hourly counts of pedestrians from 4 sensors around Melbourne: Birrarung
Marr, Bourke Street Mall, Flagstaff station, and Spencer St-Collins St (south), recorded from January
1st 2016 at 00:00:00 to December 31st 2016 at 23:00:00. 

The data is made free and publicly available from https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/b2ak-trbp

####  Usage 
<pre><code>

data(pedestrian)
</code></pre>

#### Format
A tibble with 37,700 rows and 9 variables:

* hourly_counts (integer) the number of pedestrians counted at that sensor at that time
* date_time (POSIXct, POSIXt) The time that the count was taken
* year (integer) Year of record
* month (factor) Month of record as an ordered factor (1 = January, 12 = December)
* month_day (integer) Full day of the month
* week_day (factor) Full day of the week as an ordered factor (1 = Sunday, 7 = Saturday)
* hour (integer) The hour of the day in 24 hour format
* sensor_id (integer) the id of the sensor
* sensor_name (character) the full name of the sensor

#### Source
https://data.melbourne.vic.gov.au/Transport-Movement/Pedestrian-volume-updated-monthly-/
b2ak-trbp


#### Examples 
```{r}

# explore the missingness with vis_miss
library(naniar)
vis_miss(pedestrian)
# Look at the missingness in the variables
miss_var_summary(pedestrian)
# There is only missingness in hourly_counts
# Look at the missingness over a rolling window
library(ggplot2)
gg_miss_span(pedestrian, hourly_counts, span_every = 3000)

```