
---
title: "``naniar::prop-miss-complete-var``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

Proportion of variables containing missings or complete values

####  Description 

Calculate the proportion of variables that contain a single missing or complete values.

####  Usage 
<pre><code>

prop_miss_var(data)
prop_complete_var(data)
</code></pre>
#### Arguments 

* ``data``:  a dataframe

#### Value 

numeric the proportion of variables that contain missing or complete data

#### See Also 

pct_miss_case() prop_miss_case() pct_miss_var() prop_miss_var() pct_complete_case()
prop_complete_case() ``pct_complete_var()``,``prop_complete_var()``, miss_prop_summary() miss_
case_summary ``miss_var_table``, ``n_complete``, ``n_complete_row`` miss_var_run miss_var_span
miss_var_summary miss_var_table

#### Examples 
```{r}

prop_miss_var(riskfactors)
prop_miss_var(oceanbuoys)
prop_complete_var(riskfactors)
prop_complete_var(oceanbuoys)
```
