---
title: "``naniar::
scoped-impute_median ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```
Scoped variants of impute_median

####  Description 

impute_median imputes the median for a vector. To get it to work on all variables, use impute_median_all.
To only impute variables that satisfy a specific condition, use the scoped variants, impute_below_at,
and ``impute_below_if``. To use ``_at`` effectively, you must know that ``_at`` affects variables selected with a character

####  Usage 
<pre><code>

impute_median_all(.tbl)
impute_median_at(.tbl, .vars)
impute_median_if(.tbl, .predicate)
</code></pre>

#### Arguments 

* ``.tbl``: a data.frame
* ``.vars``: variables to impute
* ``.predicate``: variables to impute

#### Value 

an dataset with values imputed

#### Examples 
```{r}

# select variables starting with a particular string.
library(dplyr)
impute_median_all(airquality)

impute_median_at(airquality,.vars = c("Ozone", "Solar.R"))
impute_median_at(airquality,.vars = vars(Ozone))
impute_median_if(airquality,.predicate = is.numeric)
```


```{r}
library(ggplot2)

airquality %>%
  bind_shadow() %>%
  impute_median_all() %>%
  add_label_shadow() %>%
  ggplot(aes(x = Ozone,y = Solar.R,colour = any_missing)) +
  geom_point()
## End(Not run)
```
