
---
title: "``naniar::impute_below_at``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

``impute_below_at``: Scoped variants of impute_below

####  Description 

impute_below operates on all variables. To only impute variables that satisfy a specific condition, use the scoped variants, ``impute_below_at``, and ``impute_below_if``. To use _at effectively, you
must know that _at`` affects variables selected with a character vector, or with vars()'.

####  Usage 
<pre><code>

impute_below_at(.tbl, .vars, prop_below = 0.1, jitter = 0.05, ...)
</code></pre>
#### Arguments 

* .tbl a data.frame
* .vars variables to impute
* prop_below the degree to shift the values. default is
* jitter the amount of jitter to add. default is 0.05
* ... extra arguments

#### Value 

an dataset with values imputed

#### Examples 
```{r}

# select variables starting with a particular string.
library(dplyr)
impute_below_at(airquality,
.vars = c("Ozone", "Solar.R"))
impute_below_at(airquality,
.vars = 1:2)
#'
impute_below_at(airquality,
.vars = vars(Ozone))
## Not run:
library(ggplot2)
airquality %>%
bind_shadow() %>%
impute_below_at(vars(Ozone, Solar.R)) %>%
add_label_shadow() %>%
ggplot(aes(x = Ozone,
y = Solar.R,
colour = any_missing)) +
geom_point()
## End(Not run)
```
