
---
title: "``naniar::oceanbuoys``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

## oceanbuoys 

West Pacific Tropical Atmosphere Ocean Data, 1993 & 1997.

####  Description 

Real-time data from moored ocean buoys for improved detection, understanding and prediction of El Ni'o and La Ni'a. The data is collected by the Tropical Atmosphere Ocean project (http:
//www.pmel.noaa.gov/tao/index.shtml).

####  Usage 
<pre><code>
data(oceanbuoys)
</code></pre>

Format
An object of class tbl_df (inherits from tbl, data.frame) with 736 rows and 8 columns.

#### Details
Format: a data frame with 736 observations on the following 8 variables.

* ``year``: A numeric with levels 1993 1997.
* ``latitude``: A numeric with levels -5 -2 0.
* ``longitude``: A numeric with levels -110 -95.
* ``sea_temp_c``: Sea surface temperature(degree Celsius), measured by the TAO buoys at one meter
below the surface.
* ``air_temp_c``: Air temperature(degree Celsius), measured by the TAO buoys three meters above the
sea surface.
* ``humidity``: Relative humidity( meters above the sea surface.
* ``wind_ew``: The East-West wind vector components(M/s). TAO buoys measure the wind speed and direction four meters above the sea surface. If it is positive, the East-West component of the
wind is blowing towards the East. If it is negative, this component is blowing towards the West.
* ``wind_ns``: The North-South wind vector components(M/s). TAO buoys measure the wind speed and direction four meters above the sea surface. If it is positive, the North-South component of the
wind is blowing towards the North. If it is negative, this component is blowing towards the South.

#### Source
http://www.pmel.noaa.gov/tao/data_deliv/deliv.html

#### See Also 

library(MissingDataGUI) (data named "tao")

#### Examples 
```{r}

# explore the missingness with vis_miss
library(naniar)
vis_miss(oceanbuoys)
# Look at the missingness in the variables
miss_var_summary(oceanbuoys)
# Look at the missingness in air temperature and humidity
library(ggplot2)
p <-
ggplot(oceanbuoys,
aes(x = air_temp_c,
pct-miss-complete-case 63
y = humidity)) +
geom_miss_point()
p
# for each year?
p + facet_wrap(~year)
# this shows that there are more missing values in humidity in 1993, and
# more air temperature missing values in 1997
# what if we explore the value of air temperature and humidity based on
# the missingness of each
oceanbuoys %>%
bind_shadow() %>%
ggplot(aes(x = air_temp_c,
fill = humidity_NA)) +
geom_histogram()
oceanbuoys %>%
bind_shadow() %>%
ggplot(aes(x = humidity,
fill = air_temp_c_NA)) +
geom_histogram()
```
