---
title: "``gg_miss_fct ``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(naniar)
```

Plot the number of missings for each variable, broken down by a factor

####  Description 

This function draws a ggplot plot of the number of missings in each column, broken down by a
categorical variable from the dataset. A default minimal theme is used, which can be customised as
normal for ggplot.

####  Usage 
<pre><code>
gg_miss_fct(x, fct)
</code></pre>

#### Arguments 

* ``x``: data.frame
* ``fct``: column containing the factor variable to visualise

#### Examples 
```{r}
gg_miss_fct(x = riskfactors, fct = marital)
library(ggplot2)
gg_miss_fct(x = riskfactors, fct = marital) + labs(title = "NA in Risk Factors and Marital status")
```

#### Value 

ggplot object depicting the each variable.

#### See Also 

``geom_miss_point()``,``gg_miss_case()``,``gg_miss_case_cumsum``,``gg_miss_span()``,``gg_miss_var()``,``gg_miss_var_cumsum()``,``gg_miss_which()``